Dealing with Consumer Uncertainty: Online Product Reviews and What makes them helpful?

### 2022-09-07 Paper.Rmd
extend search/exp framework

-   I am extending it atm

@@

In order to solve this problem @nelson1970 differentiated goods based on their search and experience attributes [@nelson1974economic; @nelson1974; @nelson1981]. Search Attributes are the qualities that can be assessed before purchase. On the contrary, Experience Attributes can only be assessed by using the product itself, in other words, evaluation is only possible after purchase. A single good can have both search and experience attributes. Depending on its dominant attributes the good can be classified as Search or Experience. @darby1973 extended Search and Experience goods framework with Credence goods where consumers can't evaluate the good even after consumption.

-   you were about to define what search is and when it is not effective

A product's Total Cost consists of both Search Cost and Product Cost. This Search Cost is higher for Experience Goods, in other words, information search is costlier for Experience Goods than Search Goods.

To explain it in a more generalized way, let's also define what "search" is. @nelson1970 defines search as "The most obvious procedure available to the consumer in obtaining information about price or quality is search". People will always prefer sampling or trial use given the fact that the cost of the sampling or trial is lower than the cost of the search. This is why search is costlier for Experience Goods. For instance, getting information about a car (test drive, guides on the web etc.) is less costly than actually buying it. Even though a car has experience attributes, with this logic it is considered as a search good [@klein1998].

-   might explain that goods within the same group can show different characteristics

>>>>

@@

In order to solve this problem @nelson1970 differentiated goods based on their search and experience attributes [@nelson1974economic; @nelson1974; @nelson1981]. Search Attributes are the qualities that can be assessed before purchase. On the contrary, Experience Attributes can only be assessed by using the product itself, in other words, evaluation is only possible after purchase. A single good can have both search and experience attributes. Depending on its dominant attributes the good can be classified as Search or Experience. @darby1973 extended Search and Experience goods framework with Credence goods where consumers can't evaluate the good even after the consumption. Though, Credence goods won't be discussed any further in this study.

Consumers can choose from two different strategies when they want to acquire more information about products. Consumers "search" in order to get information about a product assuming that they perfectly know where they can obtain the knowledge. @nelson1970 defines the search process as *"The most obvious procedure available to the consumer in obtaining information about price or quality is search"*. The search process is complete when consumers inspect the option and that inspection happens before the purchase. Contrary to the search process, consumer may choose to "experience" the product. The consumer follows this strategy when the search for information is either inappropriate, inefficient or costly compared to just experiencing the good. This is true for cheap goods especially. For instance, in order to find out the best chocolate in the market it's best for the consumer to buy every other brand available and taste them. Thus, consumers will always prefer sampling or trial use given the fact that the cost of the sampling or trial is lower than the cost of the search. This is why search is costlier for Experience goods. Therefore, the kind of strategy that a consumer chooses depends on the product's Search or Experience attributes and how dominant these attributes are.

@nelson1970 also states that consumers can use other consumers' experiences in their search processes. The information about a certain good is usually acquired in the form of "word-of"mouth" in this kind of search process. This type of search is viable when getting the information about a certain product is much more costly by "experience" compared to by "search". @klein1998 discusses that experience sharing becomes easier with the increasing usage of the internet. Because experiences about products can be shared much more easily on the internet, consumers' pre-purchase behavior might change accordingly. The reason of this is that internet decreases search costs considerably. Furthermore, the potential consumer may engage in "vicarious learning" where he/she gets indirect usage experience through the experiences of other consumers in the search process [@murray1991].

Ultimately, to put the theory in a more generalized way, a product's Total Cost consists of both Search Cost and Product Cost. This Search Cost is higher for Experience goods, in other words, information search is costlier for Experience goods than Search goods. In the consumer's perspective, to make the search viable, the marginal benefit of an additional search must be grater than the marginal cost of the additional search. The increasing use of internet decreases the search costs. Because of the decreased search costs, the consumer may undertake more search processes and this might change how people perceive good types, in other words, internet and virtual experience sharing can convert some Experience goods to Search goods [@klein1998].
